Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-05-24 paper/AlignedIsotropicGW.tex
Close #33, shared P(a).

Each of our models for the merging \ac{BBH} spin population assumes
that the merging black holes are of equal mass (this is marginally
consistent with the three observations\cite{O1-BBH}, and the $\chieff$
distribution is not particularly sensitive to the mass ratio between
the merging objects---see Methods Section \ref{sec:mass-ratio}).  We
assume that the population spin distribution factorises into a
distribution for the spin magnitude $a$ and a distribution for the
spin angles.  Finally, we assume that the distribution of spins is
common to each component in a merging binary.  Choosing one of three
magnitude distributions (see Methods Section
\ref{methsec:chieff-spin-magnitude}), ``low'' (mean $a = 0.33$,
standard deviation $0.24$), ``flat'' (mean $a = 0.5$, standard
deviation $0.29$), ``high'' (mean $a = 0.67$, standard deviation
$0.24$) and pairing with either an isotropic angular distribution or a
distribution that generates perfect alignment with the positive $z$
axis yields six different models for the $\chieff$ distribution.
These models are shown in Figure \ref{fig:chieff-distribution-models}.
While the Advanced LIGO searches use spin-aligned templates they are
efficient in detecting misaligned binary black hole
systems\cite{2016PhRvD..93l2003A}; we assume here that the $\chieff$
distribution of observed sources follows the true population.

>>>>

Each of our models for the merging \ac{BBH} spin population assumes
that the merging black holes are of equal mass (this is marginally
consistent with the three observations\cite{O1-BBH}, and the $\chieff$
distribution is not particularly sensitive to the mass ratio between
the merging objects---see Methods Section \ref{sec:mass-ratio}).  We
assume that the population spin distribution factorises into a
distribution for the spin magnitude $a$ and a distribution for the
spin angles.  Finally, we assume that the distribution of spins is
common to each component in a merging binary (in reality the
distributions of spin for each component in the binary may differ
systematically due to different formation and accretion histories, but
our analysis is not sensitive to the magnitude distribution at this
level; see below).  Choosing one of three magnitude distributions (see
Methods Section \ref{methsec:chieff-spin-magnitude}), ``low'' (mean
$a = 0.33$, standard deviation $0.24$), ``flat'' (mean $a = 0.5$,
standard deviation $0.29$), ``high'' (mean $a = 0.67$, standard
deviation $0.24$) and pairing with either an isotropic angular
distribution or a distribution that generates perfect alignment with
the positive $z$ axis yields six different models for the $\chieff$
distribution.  These models are shown in Figure
\ref{fig:chieff-distribution-models}.  While the Advanced LIGO
searches use spin-aligned templates they are efficient in detecting
misaligned binary black hole systems\cite{2016PhRvD..93l2003A}; we
assume here that the $\chieff$ distribution of observed sources
follows the true population.
